\epigraph{\textit{No amount of experimentation can ever prove me right; a single experiment can prove me wrong.}}{-- \textup{Albert Einstein}}

\section{Methodology}

For us to evaluate the performance of our proposed method, we need to compare it with the state-of-the-art tools we showed in Chapter \ref{chapter:related}. For us to do so, we need to have a set of experiments that we can run on the same software environment. We also need to have a bunch of datasets that we can use to run the experiments. In this chapter, we will describe the methodology we have followed to conduct the experiments, as well as the datasets that are subject to the test. For us to achieve this, we will answer the questions posed in Chapter \ref{chapter:intro}, namely, the project goals (see section \ref{section:objectives}).

\begin{enumerate}
    \itemsep0.5em
    \item To evaluate how the \textit{subsetting} tool has been improved, we need to run the \textit{subsetting} tool on the same software environment as the one used in the original paper. We will use the \textit{ETL} tool to compress the Wikidata JSON dump to a size that is manageable for the \textit{Pregel} algorithm. This is, we will try to tell if the tool has been improved in terms of the hardware needed to run it. Recall that for Labra's \cite{https://doi.org/10.48550/arxiv.2110.11709} solution to work, a costly machine with 4TB of RAM is required. We will verify if our solution can run on commodity hardware. In this case, the test is just to evaluate if the tool can run on commodity hardware, not to compare the performance of the tool with other tools.
    \item To evaluate how the \textit{subsetting} tool has been improved, we need to measure the time it takes to subset the Wikidata JSON dump. We will compare the time it takes to subset the dump with the time it takes to subset the Wikidata JSON dump using the original tool. For us to have a fair comparison, we will run the experiments three times and take the average of the results.
    \item To evaluate how the \textit{subsetting} tool has been improved, we will try to subset other RDF datasets, apart from the Wikidata JSON dump. This is, we will try to tell if the tool is generic enough to subset other RDF Knowledge graphs. In this case, the test is just to evaluate if the tool can subset other RDF datasets, not to compare the performance of the tool with other tools.
\end{enumerate}

\section{Hardware}

For us to run the experiments, we need to have a machine with enough resources to run them, but with reasonable specifications. Hence, we will use a machine proprietary of the \textit{Web Semantic Research Group} (WESO) of the \textit{University of Oviedo}. The machine has the following characteristics:

\begin{itemize}
    \itemsep0.5em
    \item \textbf{CPU}: Intel(R) Xeon(R) Silver 4214 CPU @ 2.20GHz (12 cores and 24 threads)
    \item \textbf{RAM}: 40GB
    \item \textbf{OS}: Ubuntu 20.04.3 LTS
\end{itemize}

\section{Datasets}

To test the above questions, we will use two types of datasets, namely, Wikidata JSON dumps and RDF datasets. We will use the Wikidata JSON dumps from 2017-08-21 to test the \textit{ETL} tool, and we will use both for the \textit{subsetting} tool. For us to compare our solution with the original one, we will use this same dataset to test the \texttt{wdsub}\footnote{\url{https://github.com/weso/wdsub/tree/master/examples}} tool. What's more, apart from the Wikidata JSON dumps, we will use other RDF datasets to test the \textit{subsetting} tool and check whether \texttt{pschema-rs} is generic enough to subset other RDF Knowledge graphs. According to this, we will use the \textit{Uniprot} dataset\footnote{\url{https://ftp.uniprot.org/pub/databases/uniprot/current_release/rdf/}}, which is a database that contains information about proteins~\cite{10.1093/nar/gkac1052}. We will use a \texttt{uniprotkb\_reviewed} dataset as those are the most relevant ones. Note that the serialization format of the \textit{Uniprot} dumps is \texttt{RDF/XML}, as such, we will use the \texttt{riot} command line utility from \textit{Apache Jena} to convert from \texttt{RDF/XML} to \texttt{N-Triples}. Refer to the examples in the Github repository\footnote{\url{https://github.com/angelip2303/pschema-rs/tree/main/examples/from_uniprot}} for more information. There, you will find the \texttt{run.sh} script that will execute the \textit{subsetting} tool on the \textit{Uniprot} dataset automatically.